---
title: "Introduction to ksrlive"
author: "Westa Domanova"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Data

This package contains a part of the phosphoproteomics data from 
[Humphrey *et al.*, Cell Metabolism, 2013](http://dx.doi.org/10.1016/j.cmet.2013.04.010).   

```{r, phospho-data}
# library(ksrlive)
devtools::load_all("~/Desktop/ksrlive") # replace this with top line at the end
data(datalist)
#head(data_kin)
head(data_df)
```

Also included in this package is an integrated database of site specific kinase 
substrate relationships. The databases used were: [PhosphositePLUS](http://www.phosphosite.org/), downloaded 2014/06/23, [PhosphoELM](http://phospho.elm.eu.org/) release 9.0, [PhosphoPOINT]() 04/2014 and [Human Protein Reference Database](http://www.hprd.org/) release 9.
```{r, ssksr-data}
data(phosphonetwork)
head(phosphonetwork.df)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
